### 2012-05-12 inst/examples/cost_of_underestimating.Rmd
updated example with cost of underestimating (and fixed jekyll rendering in earlier examples

``` {r  echo=FALSE, cache=FALSE }
render_jekyll()
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.  The true uncertainty is much smaller than that assumed, just a small uncertainty in growth.  We compare the case where the uncertainty is equal to this tiny growth uncertainty to policies derived under much greater uncertainty assumptions, and see how the resulting profit varies.

@@

We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).  This provides a look-up table for the dynamic programming calculations.

In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.  Simulation turns out to be more efficient than numerically integrating over each distribution.

## No Uncertainty

@@

``` {r  simulate }
sims_known <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
````
Find the transition matrix

@@

Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
})
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty and compare the results.

@@

## Ignoring uncertainty

@@

``` {r  simulate }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
sims_known <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1
````
Find the transition matrix

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1

sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

### 2012-05-12 inst/examples/value_of_information.Rmd
updated example with cost of underestimating (and fixed jekyll rendering in earlier examples

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`

``` {r  echo=FALSE, cache=FALSE }
render_jekyll()
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````
